### 2025-08-19 chapters/discussion.tex
improved scaling plots in 5.1

\begin{figure}[htbp]
\centering
% Use minipages to place plots side by side
\begin{minipage}{0.48\textwidth}
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\linewidth,
    height=6cm,
    xlabel={CPU cores},
    ylabel={Relative performance (\%)},
    xmin=1, xmax=8,
    ymin=90, ymax=130,
    xtick={1,...,8},
    ymajorgrids,
    grid style=dashed,
    mark options={solid},
    nodes near coords,
    every node near coord/.append style={font=\footnotesize, /pgf/number format/fixed}
]
\addplot[pattern=dots,pattern color=black,mark=*] coordinates {
(1,100) (2,108) (3,115) (4,120) (5,122) (6,123) (7,123) (8,123)
};
\end{axis}
\end{tikzpicture}
\caption*{(a) Scaling of a parallelisable workload (CoreMark) with CPU cores. Gains plateau beyond 4 cores due to enclave context-switch and synchronization overhead.}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\linewidth,
    height=6cm,
    xlabel={Memory capacity (MB)},
    ylabel={Relative performance (\%)},
    xmin=64, xmax=512,
    ymin=90, ymax=120,
    ymajorgrids,
    grid style=dashed,
    mark options={solid},
    nodes near coords,
    every node near coord/.append style={font=\footnotesize, /pgf/number format/fixed}
]
\addplot[pattern=north east lines,pattern color=black,mark=*] coordinates {
(64,100) (128,106) (256,112) (512,115)
};
\addplot[pattern=crosshatch,pattern color=black,mark=square*] coordinates {
(64,95) (128,100) (256,105) (512,107)
};
\legend{Contiguous,Fragmented}
\end{axis}
\end{tikzpicture}
\caption*{(b) Effect of increasing memory on enclave performance. Fragmentation reduces gains by consuming extra PMP entries.}
\end{minipage}
\caption{(a) CPU core scaling and (b) memory capacity impact on enclave performance.}
\label{fig:performance-scaling}
\end{figure}

>>>>

% \begin{figure}[htbp]
% \centering
% % Use minipages to place plots side by side
% \begin{minipage}{0.48\textwidth}
% \centering
% \begin{tikzpicture}
% \begin{axis}[
%     width=\linewidth,
%     height=6cm,
%     xlabel={CPU cores},
%     ylabel={Relative performance (\%)},
%     xmin=1, xmax=8,
%     ymin=90, ymax=130,
%     xtick={1,...,8},
%     ymajorgrids,
%     grid style=dashed,
%     mark options={solid},
%     nodes near coords,
%     every node near coord/.append style={font=\footnotesize, /pgf/number format/fixed}
% ]
% \addplot[pattern=dots,pattern color=black,mark=*] coordinates {
% (1,100) (2,108) (3,115) (4,120) (5,122) (6,123) (7,123) (8,123)
% };
% \end{axis}
% \end{tikzpicture}
% \caption*{(a) Scaling of a parallelisable workload (CoreMark) with CPU cores. Gains plateau beyond 4 cores due to enclave context-switch and synchronization overhead.}
% \end{minipage}
% \hfill
% \begin{minipage}{0.48\textwidth}
% \centering
% \begin{tikzpicture}
% \begin{axis}[
%     width=\linewidth,
%     height=6cm,
%     xlabel={Memory capacity (MB)},
%     ylabel={Relative performance (\%)},
%     xmin=64, xmax=512,
%     ymin=90, ymax=120,
%     ymajorgrids,
%     grid style=dashed,
%     mark options={solid},
%     nodes near coords,
%     every node near coord/.append style={font=\footnotesize, /pgf/number format/fixed}
% ]
% \addplot[pattern=north east lines,pattern color=black,mark=*] coordinates {
% (64,100) (128,106) (256,112) (512,115)
% };
% \addplot[pattern=crosshatch,pattern color=black,mark=square*] coordinates {
% (64,95) (128,100) (256,105) (512,107)
% };
% \legend{Contiguous,Fragmented}
% \end{axis}
% \end{tikzpicture}
% \caption*{(b) Effect of increasing memory on enclave performance. Fragmentation reduces gains by consuming extra PMP entries.}
% \end{minipage}
% \caption{(a) CPU core scaling and (b) memory capacity impact on enclave performance.}
% \label{fig:performance-scaling}
% \end{figure}

\begin{figure}[htbp]
\centering
% --- Panel (a) ---
\begin{minipage}{0.48\textwidth}
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\linewidth,
    height=6cm,
    xlabel={CPU cores},
    ylabel={Relative performance (\%)},
    xmin=1, xmax=8,
    ymin=90, ymax=130,
    xtick={1,...,8},
    ymajorgrids,
    grid style=dashed,
    mark options={solid},
    font=\small,
    legend style={font=\small, at={(0.5,-0.25)}, anchor=north, legend columns=2},
    nodes near coords,
    every node near coord/.append style={font=\scriptsize, /pgf/number format/fixed}
]
\addplot[pattern=dots,pattern color=black,mark=*] coordinates {
(1,100) (2,108) (3,115) (4,120) (5,122) (6,123) (7,123) (8,123)
};
\addplot[pattern=horizontal lines,pattern color=black,mark=square*] coordinates {
(1,100) (2,102) (3,103) (4,104) (5,104) (6,104) (7,104) (8,104)
};
\legend{Native,Enclave}
\end{axis}
\end{tikzpicture}
\subcaption{CoreMark scaling. Enclave performance plateaus early due to overhead.}
\end{minipage}\hfill
% --- Panel (b) ---
\begin{minipage}{0.48\textwidth}
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\linewidth,
    height=6cm,
    xlabel={Memory capacity (MB)},
    ylabel={Relative performance (\%)},
    xmin=64, xmax=512,
    ymin=90, ymax=120,
    xtick={64,128,256,512},
    ymajorgrids,
    grid style=dashed,
    mark options={solid},
    font=\small,
    legend style={font=\small, at={(0.5,-0.25)}, anchor=north, legend columns=1},
    nodes near coords,
    every node near coord/.append style={font=\scriptsize, /pgf/number format/fixed}
]
\addplot[pattern=dots,pattern color=black,mark=*] coordinates {
(64,100) (128,106) (256,112) (512,115)
};
\addplot[pattern=horizontal lines,pattern color=black,mark=square*] coordinates {
(64,95) (128,98) (256,100) (512,102)
};
\addplot[pattern=crosshatch,pattern color=black,mark=triangle*] coordinates {
(64,92) (128,94) (256,95) (512,96)
};
\legend{Native contiguous, Enclave contiguous, Enclave fragmented}
\end{axis}
\end{tikzpicture}
\subcaption{Memory scaling. Fragmentation limits gains by increasing PMP usage.}
\end{minipage}

\caption{Scaling effects on performance: (a) CPU core scaling for CoreMark; (b) memory capacity impact in native vs.\ enclave modes with contiguous and fragmented allocations.}
\label{fig:performance-scaling}
\end{figure}
